### 2016-05-11 lineups.Rnw
figures

<<get_sm_friends, echo=FALSE, fig.width=8, fig.height=3, message = FALSE, warning = FALSE>>=
source("Code/small_friends.R")
ggplot(data= view_rs2, aes(x = x, y=y)) + 
  geom_tile(aes(fill = as.factor(value))) + scale_fill_manual(values = c('white', 'black')) +
  geom_rect(data= NULL, inherit.aes = FALSE, 
            aes(xmin = 20, xmax = 35, ymin = 20, ymax = 35, fill =NA), color = 'red') + 
  facet_wrap(~wave) + theme_bw() + 
  theme(aspect.ratio=1)

@

The first wave of the network, which is conditioned on in estimation, is given below.

<<wave1, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3>>=
library(sna)
library(network)
actual1 <- merge(data.frame(as.edgelist(as.network(fd2.w1))), 
                 data.frame(id = 1:16, drink = drink2[,1]), 
                 by.x = "X1", by.y = "id", all = T)
for (j in 1:nrow(actual1)){
      if (!(actual1$X1[j] %in% actual1$X2) & is.na(actual1$X2[j])){
        actual1$X2[j] <- actual1$X1[j]
      } else {actual1$X2[j] <- actual1$X2[j]}
}
actual2 <- merge(data.frame(as.edgelist(as.network(fd2.w2))), 
                 data.frame(id = 1:16, drink = drink2[,2]), 
                 by.x = "X1", by.y = "id", all = T)
for (j in 1:nrow(actual2)){
      if (!(actual2$X1[j] %in% actual2$X2) & is.na(actual2$X2[j])){
        actual2$X2[j] <- actual2$X1[j]
      } else {actual2$X2[j] <- actual2$X2[j]}
    }
actual1$wave <- 1
actual2$wave <- 2

waves <- rbind(actual1, actual2)
library(geomnet)
ggplot(data = actual1, aes(from_id = X1, to_id = X2)) + 
  geom_net(label = TRUE, hjust = -.5, labelcolour = 'black', fiteach = T,
           aes(color = as.factor(drink))) + 
  theme_net() 
#ggplot(data = waves, aes(from_id = X1, to_id = X2)) + 
#  geom_net(label = TRUE, hjust = -.5, labelcolour = 'black', fiteach = T,
#           aes(color = as.factor(drink))) + 
#  theme_net() + theme(panel.background = element_rect(fill = "white", color = 'black')) + facet_wrap(~wave)
@

@@

\begin{table}[h]
\caption{\label{tab:models}Parameters and estimates of models $M_1$, $M_2$, and $M_3$. Estimates are the mean of 1000 iterations of the model estimates. The lineups that follow are simulated from models using these values.}
\centering
\scalebox{0.8}{
\begin{tabular}{lccrrr}
Effect name & Parameter & Corresponding Statistic & $M_1$ Estimate & $M_2$ Estimate & $M_3$ Estimate\\
\hline
\hline
Rate 1 (wave 1 $\rightarrow$ 2) & $\alpha_1$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_2) - x_{ij}(t_1))^2 $ & 
\Sexpr{round(null_mod_sv[1], 2)} &
\Sexpr{round(alt_mod_sv[1], 2)} & 
\Sexpr{round(alt_mod2_sv[1], 2)} 
\\
Rate 2 (wave 2 $\rightarrow$ 3) & $\alpha_2$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_3) - x_{ij}(t_2))^2 $ & 
\Sexpr{round(null_mod_sv[2], 2)} &
\Sexpr{round(alt_mod_sv[2], 2)} & 
\Sexpr{round(alt_mod2_sv[2], 2)}
\\
Outdegree & $\beta_1$ & $s_{i1}(x) = \sum\limits_{j=1}^n x_{ij}$ & 
\Sexpr{round(null_mod_sv[3], 2)} &
\Sexpr{round(alt_mod_sv[3], 2)} & 
\Sexpr{round(alt_mod2_sv[3], 2)}
\\
Reciprocity & $\beta_2$ & $s_{i2}(x) = \sum\limits_{j=1}^n x_{ij}x_{ji}$ & \Sexpr{round(null_mod_sv[4], 2)} &
\Sexpr{round(alt_mod_sv[4], 2)} & 
\Sexpr{round(alt_mod2_sv[4], 2)}
\\
Jumping Transitive Triplets & $\beta_3$ & $s_{i3}(x) = \sum\limits_{\forall j\neq h} x_{ij}x_{ih}x_{hj} \mathbb{I}(v_i = v_h \neq v_j)$ & -- & 
\Sexpr{round(alt_mod_sv[5], 2)} & -- \\
\# doubly achieved distances & $\beta_4$ & $s_{i4}(x) = |\{j : x_{ij} = 0, \sum\limits_h x_{ih}x_{hj} \geq 2\}|$ & -- & -- &
\Sexpr{round(alt_mod2_sv[5], 2)}
\end{tabular}}
\end{table}

>>>>

\begin{figure}
<<get_sm_friends, echo=FALSE, fig.width=8, fig.height=3, message = FALSE, warning = FALSE>>=
source("Code/small_friends.R")
view_rs2$wave <- factor(view_rs2$wave)
levels(view_rs2$wave) <- c("Wave 1", "Wave 2", "Wave 3")
ggplot(data= view_rs2, aes(x = x, y=y)) + 
  geom_tile(aes(fill = as.factor(value))) + 
  scale_fill_manual("X likes Y", labels=c("no", "yes"), values = c('white', 'black')) +
  geom_rect(data= NULL, inherit.aes = FALSE, 
            aes(xmin = 20, xmax = 35, ymin = 20, ymax = 35, fill =NA), color = 'red') + 
  facet_wrap(~wave) + theme_bw() + 
  theme(aspect.ratio=1) 
@
\caption{\label{fig:smallfriends}Representation of the edge matrix in waves 1,2, and 3 of the friendship study \hh{XXX cite XXX}. \hh{x and y axes labels are not particularly informative.}}
\end{figure}

The first wave of the network, which is conditioned on in estimation, is given in Figure~\ref{fig:wave1}.

\begin{figure}
\centering
<<wave1, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, out.width='.6\\linewidth'>>=
library(sna)
library(network)
actual1 <- merge(data.frame(as.edgelist(as.network(fd2.w1))), 
                 data.frame(id = 1:16, drink = drink2[,1]), 
                 by.x = "X1", by.y = "id", all = T)
for (j in 1:nrow(actual1)){
      if (!(actual1$X1[j] %in% actual1$X2) & is.na(actual1$X2[j])){
        actual1$X2[j] <- actual1$X1[j]
      } else {actual1$X2[j] <- actual1$X2[j]}
}
actual2 <- merge(data.frame(as.edgelist(as.network(fd2.w2))), 
                 data.frame(id = 1:16, drink = drink2[,2]), 
                 by.x = "X1", by.y = "id", all = T)
for (j in 1:nrow(actual2)){
      if (!(actual2$X1[j] %in% actual2$X2) & is.na(actual2$X2[j])){
        actual2$X2[j] <- actual2$X1[j]
      } else {actual2$X2[j] <- actual2$X2[j]}
    }
actual1$wave <- 1
actual2$wave <- 2

waves <- rbind(actual1, actual2)
library(geomnet)
actual1$behaviour <- factor(actual1$drink)
levels(actual1$behaviour) <- c("None", "Once or twice a year", "Once a month", "Once a week")
ggplot(data = actual1, aes(from_id = X1, to_id = X2)) + 
  geom_net(label = TRUE, hjust = 0.5, vjust=0.5, size=10,  
           fiteach = T, labelcolour = 'black',
           aes(colour = behaviour)) + 
  scale_colour_brewer("Drinking behavior", palette="YlOrRd") +
  theme_net() 
#ggplot(data = waves, aes(from_id = X1, to_id = X2)) + 
#  geom_net(label = TRUE, hjust = -.5, labelcolour = 'black', fiteach = T,
#           aes(color = as.factor(drink))) + 
#  theme_net() + theme(panel.background = element_rect(fill = "white", color = 'black')) + facet_wrap(~wave)
@
\caption{\label{fig:wave1} Network of friendships of wave 1 of the subset of students marked in Figure~\ref{fig:smallfriends}. }
\end{figure}

@@

\begin{table}[h]
\caption{\label{tab:models}Parameters and estimates of models $M_1$, $M_2$, and $M_3$. Estimates are the mean of 1000 iterations of the model estimates. The lineups that follow are simulated from models using these values.}
\centering
\scalebox{0.8}{
\begin{tabular}{lccrrr}
Effect name & Parameter & Corresponding Statistic & $M_1$  & $M_2$  & $M_3$ \\
\hline
\hline
Rate 1 (wave 1 $\rightarrow$ 2) & $\alpha_1$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_2) - x_{ij}(t_1))^2 $ & 
\Sexpr{round(null_mod_sv[1], 2)} &
\Sexpr{round(alt_mod_sv[1], 2)} & 
\Sexpr{round(alt_mod2_sv[1], 2)} 
\\
Rate 2 (wave 2 $\rightarrow$ 3) & $\alpha_2$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_3) - x_{ij}(t_2))^2 $ & 
\Sexpr{round(null_mod_sv[2], 2)} &
\Sexpr{round(alt_mod_sv[2], 2)} & 
\Sexpr{round(alt_mod2_sv[2], 2)}
\\
Outdegree & $\beta_1$ & $s_{i1}(x) = \sum\limits_{j=1}^n x_{ij}$ & 
\Sexpr{round(null_mod_sv[3], 2)} &
\Sexpr{round(alt_mod_sv[3], 2)} & 
\Sexpr{round(alt_mod2_sv[3], 2)}
\\
Reciprocity & $\beta_2$ & $s_{i2}(x) = \sum\limits_{j=1}^n x_{ij}x_{ji}$ & \Sexpr{round(null_mod_sv[4], 2)} &
\Sexpr{round(alt_mod_sv[4], 2)} & 
\Sexpr{round(alt_mod2_sv[4], 2)}
\\
Jumping Transitive Triplets & $\beta_3$ & $s_{i3}(x) = \sum\limits_{\forall j\neq h} x_{ij}x_{ih}x_{hj} \mathbb{I}(v_i = v_h \neq v_j)$ & -- & 
\Sexpr{round(alt_mod_sv[5], 2)} & -- \\
\# doubly achieved distances & $\beta_4$ & $s_{i4}(x) = |\{j : x_{ij} = 0, \sum\limits_h x_{ih}x_{hj} \geq 2\}|$ & -- & -- &
\Sexpr{round(alt_mod2_sv[5], 2)}
\end{tabular}}
\end{table}
